----
----

```{r}
customer_data=read.csv("Mall_Customers.csv")
summary(customer_data)
```

```{r}
names(customer_data)

```

```{r}
head(customer_data)
summary(customer_data$Age)
```


```{r}
sd(customer_data$Age)
summary(customer_data$Annual.Income..k..)
sd(customer_data$Annual.Income..k..)
summary(customer_data$Age)
```


```{r}
sd(customer_data$Spending.Score..1.100.)

```

#####  Data Visualization

#### Gender Visualization by creating  a barplot

 
```{r}
a=table(customer_data$Gender)
barplot(a,main="Using BarPlot to display Gender Comparision",
       ylab="Count",
       xlab="Gender",
       col=rainbow(2),
       legend=rownames(a))
```
From the above barplot, we observe that the number of females is higher than the males.

#### Piechart
let us visualize a pie chart to observe the ratio of male and female distribution.

```{r}
pct=round(a/sum(a)*100)
lbs=paste(c("Female","Male")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,
   main="Pie Chart Depicting Ratio of Female and Male")
```
The percentage of females is 56%, whereas the percentage of male in the customer dataset is 44%


###### Age Visualization

```{r}
summary(customer_data$Age)

```
##### Age Visualization using Histogram

```{r}
hist(customer_data$Age,
    col="blue",
    main="Histogram to Show Count of Age Class",
    xlab="Age Class",
    ylab="Frequency",
    labels=TRUE)
```
##### Age Visualization using Boxplot

```{r}
boxplot(customer_data$Age,
       col="#ff0066",
       main="Boxplot for Descriptive Analysis of Age")
```
The maximum customer ages are between 30 and 35. The minimum age of customers is 18, whereas, the maximum age is 70.



#### Annual Income Analysis

```{r}
summary(customer_data$Annual.Income..k..)
hist(customer_data$Annual.Income..k..,
  col="#660033",
  main="Histogram for Annual Income",
  xlab="Annual Income Class",
  ylab="Frequency",
  labels=TRUE)
```

#### Density plot


```{r}
plot(density(customer_data$Annual.Income..k..),
    col="yellow",
    main="Density Plot for Annual Income",
    xlab="Annual Income Class",
    ylab="Density")
polygon(density(customer_data$Annual.Income..k..),
        col="#ccff66")
```
The minimum annual income of the customers is 15 and the maximum income is 137. People earning an average income of 70 have the highest frequency count in our histogram distribution. The average salary of all the customers is 60.56.




####   Analyzing Spending Score of the Customers



```{r}
summary(customer_data$Spending.Score..1.100.)
## Min. 1st Qu. Median Mean 3rd Qu. Max. 
## 1.00 34.75 50.00 50.20 73.00 99.00
boxplot(customer_data$Spending.Score..1.100.,
   horizontal=TRUE,
   col="#990000",
   main="BoxPlot for Descriptive Analysis of Spending Score")
```

#### Histogram


```{r}
hist(customer_data$Spending.Score..1.100.,
    main="HistoGram for Spending Score",
    xlab="Spending Score Class",
    ylab="Frequency",
    col="#6600cc",
    labels=TRUE)
```
The minimum spending score is 1, maximum is 99 and the average is 50.20. We can see Descriptive Analysis of Spending Score is that Min is 1, Max is 99 and avg. is 50.20. From the histogram, we conclude that customers between class 40 and 50 have the highest spending score among all the classes.




#### Determing the optimal number of clusters.1)Elbow Method



```{r}
library(purrr)
set.seed(123)
# function to calculate total intra-cluster sum of square 
iss <- function(k) {
  kmeans(customer_data[,3:5],k,iter.max=100,nstart=100,algorithm="Lloyd" )$tot.withinss
}
k.values <- 1:10
iss_values <- map_dbl(k.values, iss)
plot(k.values, iss_values,
    type="b", pch = 19, frame = FALSE, 
    xlab="Number of clusters K",
    ylab="Total intra-clusters sum of squares")
```
4 is the appropriate number of clusters since it seems to be appearing at the bend in the elbow plot.




####2)Average Silhouette Method


```{r}
library(cluster) 
library(gridExtra)
library(grid)
k2<-kmeans(customer_data[,3:5],2,iter.max=100,nstart=50,algorithm="Lloyd")
s2<-plot(silhouette(k2$cluster,dist(customer_data[,3:5],"euclidean")))
```

####  When n=3


```{r}
k3<-kmeans(customer_data[,3:5],3,iter.max=100,nstart=50,algorithm="Lloyd")
s3<-plot(silhouette(k3$cluster,dist(customer_data[,3:5],"euclidean")))

```

####  When n=4
```{r}
k4<-kmeans(customer_data[,3:5],4,iter.max=100,nstart=50,algorithm="Lloyd")
s4<-plot(silhouette(k4$cluster,dist(customer_data[,3:5],"euclidean")))
  
```
####  When n=5

```{r}
k5<-kmeans(customer_data[,3:5],5,iter.max=100,nstart=50,algorithm="Lloyd")
s5<-plot(silhouette(k5$cluster,dist(customer_data[,3:5],"euclidean")))
```

####  When n=6
```{r}
k6<-kmeans(customer_data[,3:5],6,iter.max=100,nstart=50,algorithm="Lloyd")
s6<-plot(silhouette(k6$cluster,dist(customer_data[,3:5],"euclidean")))

```
####  When n=7
```{r}
k7<-kmeans(customer_data[,3:5],7,iter.max=100,nstart=50,algorithm="Lloyd")
s7<-plot(silhouette(k7$cluster,dist(customer_data[,3:5],"euclidean")))

```
####  When n=8

```{r}
k8<-kmeans(customer_data[,3:5],8,iter.max=100,nstart=50,algorithm="Lloyd")
s8<-plot(silhouette(k8$cluster,dist(customer_data[,3:5],"euclidean")))
```
####  When n=9

```{r}
k9<-kmeans(customer_data[,3:5],9,iter.max=100,nstart=50,algorithm="Lloyd")
s9<-plot(silhouette(k9$cluster,dist(customer_data[,3:5],"euclidean")))
```

####  When n=10
```{r}
k10<-kmeans(customer_data[,3:5],10,iter.max=100,nstart=50,algorithm="Lloyd")
s10<-plot(silhouette(k10$cluster,dist(customer_data[,3:5],"euclidean")))
```
##### Now, we have used fviz_nbclust() function to determine and visualize the optimal number of clusters as follows –

```{r}
library(NbClust)
library(factoextra)
fviz_nbclust(customer_data[,3:5], kmeans, method = "silhouette")
```


####Gap Statistic Method.
####For computing the gap statistics method we had utilized the clusGap function for providing gap statistic as well as standard error for a given output.



```{r}

set.seed(125)
stat_gap <- clusGap(customer_data[,3:5], FUN = kmeans, nstart = 25,
            K.max = 10, B = 50)
fviz_gap_stat(stat_gap)
```

#### k6 as optimal cluster

```{r}
k6<-kmeans(customer_data[,3:5],6,iter.max=100,nstart=50,algorithm="Lloyd")
k6
```
#### Visualizing the Clustering Results using the First Two Principle Components

```{r}
pcclust=prcomp(customer_data[,3:5],scale=FALSE) #principal component analysis
summary(pcclust)
pcclust$rotation[,1:2]
```


```{r}
set.seed(1)
ggplot(customer_data, aes(x =Annual.Income..k.., y = Spending.Score..1.100.)) + 
  geom_point(stat = "identity", aes(color = as.factor(k6$cluster))) +
  scale_color_discrete(name=" ",
              breaks=c("1", "2", "3", "4", "5","6"),
              labels=c("Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5","Cluster 6")) +
  ggtitle("Segments of Mall Customers", subtitle = "Using K-means Clustering")
```


```{r}
ggplot(customer_data, aes(x =Spending.Score..1.100., y =Age)) + 
  geom_point(stat = "identity", aes(color = as.factor(k6$cluster))) +
  scale_color_discrete(name=" ",
                      breaks=c("1", "2", "3", "4", "5","6"),
                      labels=c("Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5","Cluster 6")) +
  ggtitle("Segments of Mall Customers", subtitle = "Using K-means Clustering")
```


```{r}
kCols=function(vec){cols=rainbow (length (unique (vec)))
return (cols[as.numeric(as.factor(vec))])}
digCluster<-k6$cluster; dignm<-as.character(digCluster); # K-means clusters
plot(pcclust$x[,1:2], col =kCols(digCluster),pch =19,xlab ="K-means",ylab="classes")
legend("bottomleft",unique(dignm),fill=unique(kCols(digCluster)))
```



```{r}
```


```{r}
```



```{r}
```


```{r}
```